Generative AI for image reconstruction\\ in Intensity Interferometry: a first attempt

### 2025-08-02 Phase_II/draft/main.tex
edits

\author{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen
  Basak$^{1}$, Prasenjit Saha,$^{3}$ and Subrata Sarangi$^{4,5}$}

@@

@@

\bibliographystyle{aasjournal}
\bibliography{refs}

>>>>

\author{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen
  Basak$^{1}$, {Prasenjit Saha\altaffilmark{3,*}}, and Subrata Sarangi$^{4,5}$}

@@

\altaffiltext{*}{Corresponding author; email: \href{mailto:psaha@physik.uzh.ch}{psaha@physik.uzh.ch}}

@@

\bibliographystyle{aa}
\bibliography{refs}
